\documentclass[10pt]{res}
\usepackage{scrextend}
\usepackage{helvet}
\usepackage{array}
\usepackage[a4paper, top=0.5cm, bottom=0.5cm, left=0.001cm, right=1in]{geometry}

\begin{document}
  \name{Adam Pohl \\ \\}
\begin{resume}


e-mail: adam.pohl9999@gmail.com \hfill 5 The Meadows \\
Tel: (+44) 1633 681190 \hfill Marshfield \\
Mob: (+44) 7936 363296 \hfill Cardiff \\
Date of Birth: $23^{rd}$ December 1993 \hfill CF3 2AY \\
Nationality: Welsh

\vspace{-10pt}
\textbf{\centerline{INTRODUCTION}}
\vspace{-20pt}

A Mathematics graduate from Cardiff University, with an interest
in computer programming. An instrumental member of the schools code
club, with experience of handling various managerial duties, web development and
encouraging new learners.

\vspace{-15pt}
\textbf{\centerline{ACADEMIC QUALIFICATIONS}}
\vspace{-23pt}

\textbf{Cardiff University} \hfill 2013 $-$ 2016 \\
\textbf{\textit{BSc Mathematics, Operational Research and Statistics}} \\
Modules include: Computational Statistics, Computing for Maths (Python and
Sagemath), \\ Mechanics, Multivariate Statistics, Visual Basic programming for
OR.
\\
\textbf{Rougemont School, Newport} \hfill 2011 $-$ 2013 \\
\textbf{\textit{4 A Levels}}: Maths (A*), Further Maths (B), Chemistry (B), Physics (B). \\
UCAS points: 440
\\
\textbf{St David’s Sixth Form College, Cardiff} \hfill 2010 $-$ 2011 \\
\textbf{\textit{A Levels}}: Maths, Further Maths, Chemistry, Physics, Young Engineers.
\\
\textbf{Rougemont School, Newport} \hfill 2003 $-$ 2010 \\
\textbf{\textit{9 GCSEs}}: Maths (A*), Physics (A*), Statistics (A), Chemistry (A), English
Literature (A), \\ Biology (B), English Language (B), Geography (B),
History (B), OCR Level 2 Key Skills in IT.

\vspace{-5pt}
\textbf{\centerline{PROFESSIONAL EXPERIENCE}}
\vspace{-25pt}

\textbf{Office for National Statistics} \hfill Sept 2016 $-$ present
\begin{itemize}
    \item Statistical Analyst in the Big Data team
    \item Currently on a 6 month temporay contract.
    \item Through the use of Python and R, I perform statistical analysis of \\
    interesting datasets.
\end{itemize}

\textbf{Target Group} \hfill Aug 2016 $-$ Sept 2016
\begin{itemize}
    \item 1st/2nd line IT support
    \item 1 month temporay contract.
    \item I answered the phone and setup new windows and email accounts for \\
    staff members
\end{itemize}
\textbf{Computing for Maths tutorials} \hfill Oct $-$ Dec, 2014 and 2015

\begin{itemize}
    \item After a strong performance in this course, the module leader
    specifically \\ chose me to act as a tutor. This involved the teaching of
    Python and \\ Sagemath to subsequent first year students.
\end{itemize}

\textbf{TK Maxx, Newport.} \hfill Oct 2010 $-$ Dec 2016
\begin{itemize}
    \item Part time Store Associate
    \item Financial transactions and customer relations.
\end{itemize}

\textbf{Silvertel, Newport.} \hfill Aug 2010
\begin{itemize}
    \item Electronic component testing, programming of parts.
    \item Edited web pages using Adobe Dreamweaver, mechanical assembly.
    \item Completed a stock check using SAGE, circuit drawing on Visio.
\end{itemize}

\textbf{Cricket coaching (9 $-$ 13yr olds)} \hfill 2009 $-$ present
\begin{itemize}
    \item Certified ECB level 1 cricket coach.
\end{itemize}

\vspace{-10pt}
\textbf{\centerline{RELEVANT SKILLS}}

\vspace{-20pt}
\textbf{IT/Computer Programming}
\begin{addmargin}[2em]{0em}
    In completing the `Computing for Mathematics' module, I have learnt how to
    code in python and also how to write mathematics in \LaTeX. I found this to
    be very enjoyable and as computers are an essential part of any business, I
    feel that being able to code is a valuable skill to have.
    \\[4pt]
    During my second and final years at university I undertook modules which
    taught me how to code in R and use it to perform statistical
    computing/analysis in both one and N dimensional space.
    \\[4pt]
    Over my second and thrid years at Cardiff I was involved in the setting up
    and running of a code club in the Maths department at my university. This
    has helped me to improve my web development skills through the creation and
    maintenance of the clubs' website.
    \\[4pt]
    I have been instrumental in building a web application that assists students
    in choosing modules. This is a dynamic tool with a basic database and a user
    interface implemented in JavaScript.
    \\[4pt]
    Towards the beginning of last year I became a contributor to various open
    source software used by the international programming community:
    git-control and script (used in the Atom editor) which I contribute to via
    modern software development practices including git and GitHub.
    \\[4pt]
    During my time at the ONS I have learnt how to write web scraping scripts
    in python using the modules \textit{scrapy} and \textit{requests} and also
    how to maniplutate data for statistcal analysis with the module
    \textit{Pandas}. As a team we are working in an \textbf{agile} way,
    splitting the work up into different \textit{stories} and completing them
    over a number of \textit{2 week sprints} which greatly improved my
    programming ability through the constant review and improvement process
    that working in an agile manner brings.
    \\[4pt]
    Currently I am taking two online courses, one hosted by the University of
    Helsinki on \textit{Object-Oriented Programming in Java} and one hosted on
    pluralsight on \textit{Apache Spark}, as I feel that these would
    be useful programming knowledge to have.
\end{addmargin}

\vspace{-5pt}
\textbf{Communication, Presentation and Interpersonal skills}
\begin{addmargin}[2em]{0em}
    Working in an Agile manner within my team at the ONS has helped me to
    improve my communication and \\ interpersonal skills becuase Agile is only
    effective as long as the teamates communicate clearly and presicsely with
    one and other.
    \\[4pt]
    During code club we often have `lighting talks', in which we have to go
    up to the front and present something code related to the rest of the group.
    This has helped me with my presentation and communication skills as I have
    to make sure that (a) what I am talking about is easy enough for others to
    understand and (b) I am ready for any potential questions that may be come
    about from my presentation.
\end{addmargin}

\vspace{-5pt}
\textbf{Analytical and Problem solving}
\begin{addmargin}[3em]{0em}
    As a mathematics graduate I have developed these skills fully throughout my
    modules. Furthermore my level of programming experience further evidences my
    analytical and problem solving abilities.
\end{addmargin}

\vspace{-5pt}
\textbf{Team work}
\begin{addmargin}[2em]{0em}
    One of the pieces of coursework in Computing for Maths was taking part in a
    group project. This experience has shown me that in order for any team to be
    successful, you must develop effective working relationships with all
    members of the group. It has also helped me to better understand the
    phrase: \textit{every idea is a useful idea}, because it made me recognise
    generating innovative solutions can sometimes be more meaningful and useful
    than the final outcome itself. We were able to achieve a score of 86\% by
    utilising our strengths and working together.
\end{addmargin}

\vspace{-5pt}
\textbf{Leadership}
\begin{addmargin}[2em]{0em}
    When I took part in the Young Engineers scheme, I was the leader of my
    group and helped us to become the best team in Wales that year by only
    dropping two marks overall and win the award for best presentation. At TK
    Maxx I quite often have to run the cash registers and look after/train the
    new people on this section.
    \\[4pt]
    As a founding member of code club, I often have to run it when the residing
    lecturer is unavailable. This has involved me deciding what the focus of the
    code club will be and also arranging any lighting talks that would take
    place. Another way in which I have used code club to enhance my leadership
    skills is that, like with TK Maxx, I often have to guide/teach new members
    on how to contribute to the website and also where they may have gone wrong
    with regards to any code they are writing.
\end{addmargin}

\vspace{-5pt}
\textbf{Business and Commercial Awareness}
\begin{addmargin}[2em]{0em}
    Having worked in retail for six years, I feel that I have gained a
    good commercial awareness as I have had to make sure that whatever part of
    the store I was in, it was always neat and tidy so as to make it more
    appealing to the customer. It has also given me a better business awareness
    as we have regular meetings about how the business is doing, be it my store
    or TJX Europe, and how what I do on the shop floor can help the business to
    grow.
\end{addmargin}

\vspace{-5pt}
\textbf{\centerline{INTERESTS AND ACHIEVEMENTS}}
\vspace{-12pt}

\centerline{Duke of Edinburgh Bronze award in 2009,}
\centerline{Cricket, Tennis, Golf, Reading, Computer Programming}
\centerline{Lead Young Engineers group to being the best group in Wales.}

\vspace{-5pt}
\textbf{\centerline{REFEREES}}
\vspace{-5pt}
\begin{addmargin}[7em]{0em}
    \begin{tabular}{ m{4cm} m{5cm} m{5cm} }
        Dr Vince Knight & Mr Andrew Pugh & Mr Nigel Swier \\
        Lecturer & Quality Manager & Principal Methodologist \\
        School of Mathematics & Silvertel & Office for National Statistics \\
        Cardiff University & 1 Imperial Courtyard & Government Buildings \\
        Senghennydd Road & Imperial Park & Cardiff Road \\
        Cardiff &  Newport & Newport \\
        CF24 4AG & NP10 8UL & NP10 8XG \\
        % knightva@cardiff.ac.uk & andrew.pugh@silvertel.com & nigel\_swier@hotmail.com
    \end{tabular}
\end{addmargin}

\end{resume}
\end{document}
